Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-04 paper.tex
added tool installation

            Unless building a workflow exclusively based on custom
            functions or using a monolithic workflow engine such as SPM, users
            will need to install the tools necessary for their workflow on
            their infrastructure. Depending on the workflow engine 
            selected, this may be managed by the engine or performed manually 
            by the user. Most install the dependencies themselves. Workflow engines that
            delegate tool installation to the user include: Nipype, PSOM,

        Many of these platforms have selected to be written in 
        platform-independent languages. However,  Due to the modularity of these
        frameworks, it may be necessary
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}

>>>>

            Unless building a workflow exclusively based on custom
            functions or using a monolithic workflow engine such as SPM, users
            will need to install the tools necessary for their workflow on
            their infrastructure. Depending on the workflow engine 
            selected, this may be managed by the engine or performed manually 
            by the user. Although not a direct requirement of workflows engines, 
            engines that simplify tool installation promote sharing of 
            workflows. To simplify this process, many workflow engines rely on 
            importing and running containerized workflow tools. These engines
            include: Galaxy, Toil, Netflow, Pegasus and FastR. While most 
            provide support for Docker and Singularity, Toil and Galaxy only 
            support Docker containers. All that is required by these workflow 
            engines is the URL to the image in DockerHub or SingularityHub and
            the engine will abstract the process of acquiring the container and
            running the tool.

            Alternatively, engines such as OpenMOLE use a different tool to
            sandbox the environment, known as CARE. CARE allows 
            users to make a compressed file wrapping the tool in the 
            environment it was meant to be executed on. It uses environment 
            information to simulate the system calls of the environment when
            interacting with the tool. CARE was suggested as an alternative to
            Docker as Docker requires a Docker engine to be running on each 
            node, which may not always be the case. Moreover, Docker engines 
            cannot be launched on-the-fly as they require administrative 
            privileges. However, should a user wish to run a Docker container,
            OpenMOLE provides a mechanism to run DockerHub tools in 
            unprivileged using udocker.

            Other workflow engines do not use an form of containerization to
            ensure that workflows can be shared easily amongst users. These 
            include Taverna, Make, Pydpiper, AA, SPM, PSOM, Nipype, LONI, 
            MapReduce, Spark and Dask.
            Taverna is different from the other workflow engines, however, as 
            it is webservice-based an thus it expects that a server is up, 
            running the desired version of the tool.

            As for the engines with no tool dependency setup, it is still 
            possible for the user to manually reference a container within 
            a UDF. Conversly, libraries that manage execution of containerized 
            tools, such as Boutiques, can be intergrated into these engines.

        \section{Containers}
